Landscape composition and beneficial insects

### 2020-05-06 manuscript/manuscript_outline.Rmd
Continued on Results section

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

@@

* Function-on-scalar (FOS) regression is a special type of linear model ($\hat{y}=X\beta$), where the values of the coefficients ($\beta$) are defined by a smooth function
  + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
  + This technique has been used by other authors; @galpern2020 called this ``onion-skin regression"
  + We fit our functional regression models using _mgcv_ version 1.8-31.
  + @ockinger2007 is a test

@@

@@

@@

![Landscape influence on _P. distincta_ activity density](../figures/Pardosa_distincta_fixeff.png)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)

#Helper functions
firstUpper <- function(x){
  paste0(toupper(substring(x,1,1)),substring(x,2,nchar(x)))
}

#Rounds to dig, converts to character, anything 
roundLess <- function(x,dig){
  x <- as.character(round(x,dig))
  x[x=='0'] <- paste0('<0.',strrep('0',dig-1),'1',collapse='')
  return(x)
}

```

@@

* Function-on-scalar (FOS) regression is a special type of linear model ($\hat{y}=X\beta$), where the values of the coefficients ($\beta$) are defined by a smooth function
  + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
  + This technique has been used by other authors; @galpern2020 called this ``onion-skin regression"
  + We fit our functional regression models using _mgcv_ version 1.8-31.

@@

* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition.
  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, indicating that (comparitively) low-density stands may allow faster movement of ground beetles.
  + Ditches had the lowest level of activity density
  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with early-season (June) urban land acting as a sink, but becoming a source in the mid-season (July)
  + trees and shrubs, pulse crops, and pasture.
  + Overall wetland cover had a negative influence on _P. melanarius_ abundance, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
  + Finally, _P. melanarius_ had a very strong spatial component

```{r PteMelCoefs, echo=FALSE, message=FALSE}
load('../data/PteMelMod.Rdata')
pmelRes <- summary(PteMelMod$mod3)
linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
  rownames_to_column('loc') %>% 
  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3))

smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
  rownames_to_column('Smoother') %>% 
  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:3),roundLess,dig=2) 
kable(linTerms,caption='Linear terms for _Pterostichus melanarius_',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
        digits=c(1,2,2,2,2),align='rrrrl')
kable(smTerms[c(1,2,4,5)],caption='Smooth terms for _Pterostichus melanarius_',col.names=c('Smoothing term','E.D.F.','$\\chi^2$','p'),
        digits=c(1,2,2,2),align='rrll')

```

@@

![Temporal and spatial components of _P. melanarius_ activity density](../figures/Pterostichus_melanarius_raneff.png)

@@

![Landscape influence on _P. distincta_ activity density](../figures/Pardosa_distincta_fixeff.png)
![Temporal and spatial components of _P. distincta_ activity density](../figures/Pardosa_distincta_raneff.png)

@@

![Temporal and spatial components of _P. opilio_ activity density](../figures/Opiliones_raneff.png)
